%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Marcus Whybrow}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact
    \section{\mysidestyle Contact}

    e-mail: marcus@marcuswhybrow.net      \hfill   \\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Skills
    \section{\mysidestyle Skills}
    
    \textbf{Web App Development}\vspace{-4mm}\\%
    \begin{list2}
		\item Fluent in Python and Django
		\item Advanced knowledge of the jQuery JavaScript library, including plugin development.
		\item RESTful API development
		\item Relation database design
		\item Apache and MySQL administration
    \end{list2}
	
	\textbf{System Administration}\vspace{-4mm}\\%
	\begin{list2}
		\item Ubuntu server administration experience since March 2008
		\item VMWare server 2.x real world experience since March 2008
    \end{list2}
    
	\textbf{Mobile App Development}\vspace{-4mm}\\%
    \begin{list2}
		\item Intermediate knowledge of Android app development (Java)
		\item Intermediate knowledge of iOS app development (Objective-C)
    \end{list2}
    
    \textbf{Driving License}\vspace{-4mm}\\%
    \begin{list2}
		\item Held since September 2008
		\item No convictions or offences
    \end{list2}
    
    %__________________________________________________________________________________________________________________
    % Programming Languages
    \section{\mysidestyle Programming}

    Python, Java, C, C++, Objective-C, Linux shell scripting, \LaTeX, SQL, JavaScript, HTML/CSS.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Nottingham}, Nottingham, England \vspace{2mm}\\\vspace{1mm}%
    \textsl{Computer Science BSc Hons (G400)} \hfill \textbf{September 2008 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Expected graduation date: June 2011%
        \item Part 1 average: 71\%
        \item Highest Transcript Result: 87\% in Introduction to Software Engineering
        \item Lowest Transcript Result: 52\% in Internet and Web Services (SOAP)
    \end{list2}\vspace{-1.5mm}
    
    \textbf{Arnold Hill School \& Technology College}, Nottingham, England \vspace{2mm}\\\vspace{1mm}%
    \textsl{6th Form Colledge} \hfill \textbf{September 2006 -- June 2008}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item A Levels: Computing (A), Mathematics (A), Further Mathematics (B)%
        \item AS Levels: Computing (A), Mathematics (A), Further Mathematics (B), Music (D)%
    \end{list2}\vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Experience
    \section{\mysidestyle Experience}

    \textbf{Aware Monitoring} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Python Developer}, website and application \hfill \textbf{June 2010 -- Octover 2010}\\
    Aware Monitoring provides page load time monitoring services to huge websites such as huddle.com and wiggle.com and is always on a drive to gain new customers.
	Joining Aware Monitoring over the summer period between my second and final year at University, I worked on multiple individual projects having sole responsibility for each.

	Being a new member of a small concentrated team developing and adding features to a critical application, I would create or modify code in isolation and hand over to them for integration into their more complex structure. Thus well written code and documentation was a must.
	Tasks included the following:
	\begin{itemize}
		\item Django was the framework which powered their application and it was my responsibility to convert the companies existing public facing website from the PHP based ExpressionEngine into a Django site, whilst integrating designs from a separate website design company, the result can be seen at http://awaremonitoring.com/.
		\item Rewriting ageing python utility functions which were used in support of the application.
		\item Adding features to the existing application in keeping with the all important visual style.
	\end{itemize}
	
	Additional Responsibilities: 
	\begin{itemize}
		\item Working occasional weekends during/between university semesters after the period of employment to add new features based upon earlier work.
	\end{itemize}
	
	\newpage
	\textbf{J Sainsbury's} \vspace{2mm}\\\vspace{1mm}%
	\textsl{Working Part Time, in Replenishment and as a Cashier}  \hfill \textbf{October 2007 -- December 2007}\\
	Worked over the busy christmas shopping period during the end of my 6th Form enrolment, under many different shop floor sections replenishing shelf stock, and then became a trained cashier.
	
	%__________________________________________________________________________________________________________________
    % Experiences
    \section{\mysidestyle Volunteering\\and\\Experiences}
    
    \textbf{Gardening Assistance}, Gunby Hall, Skegness, England \vspace{2mm}\\\vspace{1mm}%
    Lived in as a gardening assistant for the grounds of Gunby Hall (National Trust) in Skegness for 7 days.
    Part of the residential section of the Duke of Edinburgh gold award.
    
    \textbf{Skiing}, Les Menuires, France \vspace{2mm}\\\vspace{1mm}%
    Spent a week learning to ski on the slopes of Les Menuires. Gained a level 1 certificate along with a group of around 20 of my friends.
    A fantastic exercise in learning a new skill.
    
    \textbf{Water-sports Expedition}, Ard\`eche, France \vspace{2mm}\\\vspace{1mm}%
    Took part in, rock-climbing, pot-holing, river-walking, kayaking and a 2 day canoe expedition down the Ard\`eche
    river in a cell of 4 2-man canoes, in a flotilla of 20 cells. One of my favourite memories.
	
	%__________________________________________________________________________________________________________________
    % Open Source Projects
    \section{\mysidestyle Open-Source\\Projects}

    \textbf{TinyGraph SNMP Monitoring}\vspace{1mm}\\%
    TinyGraph is born out of the frustration of using other network monitoring tools, and sets forth with the vision that monitoring your devices should be fun. This project is written in Python using the Django framework and makes heavy use of jQuery and SVG elements.
    \vspace{-1.5mm}
    
    \textbf{AutoLibrarian Digital Library}\vspace{1mm}\\%
    AutoLibrarian is a another Python/Django project which makes use of the Google books API to bring useful information to the books which users store within it. The project also has an Android app which can scan the barcode of a book's ISBN number for easy input.
    \vspace{-1.5mm}
    
    \textbf{jQuery State Bindings}\vspace{1mm}\\%
	A plugin for the JavaScript library jQuery, which allows the grouping of event bindings. These groups can then be enabled or disabled based upon the global "state" of your page, created for use with TinyGraph.
    \vspace{-1.5mm}
    
    All projects are hosted by GitHub: {\bf https://github.com/marcuswhybrow/}
    
    %__________________________________________________________________________________________________________________
    % Achievements
    \section{\mysidestyle Achievements}

    \textbf{Duke of Edinburgh's Award}\vspace{-4mm}\\%
    \begin{itemize}
		\item Gold award collected from St. James' Palace 29th Oct 2008
		\item Silver award achieved in 2005 (aged 15)
		\item Bronze award achieved in 2004 (aged 14)
    \end{itemize}
    \vspace{-4mm}
    
    %__________________________________________________________________________________________________________________
    % Hobbies
    \section{\mysidestyle Hobbies}

    \textbf{Guitar}\vspace{-4mm}\\%
    \begin{itemize}
		\item Practice and play grade 8 rock pieces
		\item Played at 3 battle of the bands competitions, as guitarist and vocalist on stage
    \end{itemize}
    \vspace{-2mm}
    
    \textbf{Piano}\vspace{-4mm}\\%
    \begin{itemize}
		\item Obtained an official grade 2 certificate
		\item I play the first half to the grade 9 Nocturne In E-Flat Major, Op.9 No.2 by Fr\`ed\`eric Chopin.
    \end{itemize}
    \vspace{-2mm}
    
    \textbf{Photography}\vspace{-4mm}\\%
    \begin{itemize}
    		\item Actively documented all of my Duke of Edinburgh awards, with my pictures and videos.
		\item Now own a ``pro-sumer" Nikon D90 DSLR.
    \end{itemize}
    \vspace{-2mm}
    
    \textbf{Karate}\vspace{-4mm}\\%
    \begin{itemize}
    		\item Achieved 1st Que under the Federation of Shotokan Karate (brown belt with two white stripes).
		\item Trained under FSK founder Sensie Aidan Trimble (7th Dan)
    \end{itemize}
    


    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
\section{\mysidestyle Referees} 

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Dr. Julie Greensmith}       &  \textbf{Nick Barker}                   \\
Lecturer in Computer Science			  &  CEO Aware Monitoring                       \\
University of Nottingham                &  Nottingham, England                      \\
Nottingham, England                     &          \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

